Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-23 paper.qmd
Comment geom_point in Figure 5

hex_grid_coloured_scurve1 <- ggplot() + 
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5,
             size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a") +
  xlim(sc_xlims) + ylim(sc_ylims)
```

@@

hex_grid_coloured_scurve2 <- ggplot() + 
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5,
             size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b")

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5,
             size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c")

>>>>

hex_grid_coloured_scurve1 <- ggplot() + 
  # geom_point(data = umap_scurve_scaled, 
  #            aes(x = UMAP1, y = UMAP2), 
  #            alpha = 0.5,
  #            size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve1, 
    aes(x = x, y = y,
      group = hex_poly_id, 
      fill = std_counts), color = "grey70", linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  interior_annotation("a") +
  xlim(sc_xlims) + ylim(sc_ylims)
```

@@

hex_grid_coloured_scurve2 <- ggplot() + 
  # geom_point(data = umap_scurve_scaled, 
  #            aes(x = UMAP1, y = UMAP2), 
  #            alpha = 0.5,
  #            size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve2, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", 
        linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, 
    na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b")

@@

hex_grid_coloured_scurve3 <-  ggplot() + 
  # geom_point(data = umap_scurve_scaled, 
  #            aes(x = UMAP1, y = UMAP2), 
  #            alpha = 0.5,
  #            size = 0.5) + 
  geom_polygon(
    data = hex_grid_with_counts_s_curve3, 
    aes(x = x, y = y, 
        group = hex_poly_id, 
        fill = std_counts), 
        color = "grey70", linewidth=0.2) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("c")
